Final paper: Towards Proving Termination of \texttt{zelda-mosaic} Algorithms under Conditions on the Input

### 2021-05-03 paper/paper.tex
paper: clarify theorem statement

\begin{thm}[Computing the shape normalizes it]\label{Th:compute_shape_wf_normalizes}
    For all matrices \(m\), if \(m\) is well-formed than so is the following
    matrix: \(\{ \var{shape} = \func{compute\_shape}\, m; \var{contents} =
    \func{contents}\, m \}\).
\end{thm}

>>>>

\begin{thm}[Computing the shape normalizes it]\label{Th:compute_shape_wf_normalizes}
    For all matrices \(m\) with contents \(c\), if \(m\) is well-formed than so
    is the following matrix: \(\{ \var{shape} = \func{compute\_shape}\, c;
    \var{contents} = c \}\).
\end{thm}
